---
title: "Valdivian Temperate Flooded & Swamp Forest"
subtitle: "{{< fa code >}} **1.B.3.Ej.663 or M663**"
categories:
  - 1.B.3.Ej Valdivian
  - Chile
  - Argentina
execute: 
  echo: false
  warning: false
---

```{r}
library(dplyr)
here::i_am("websrc/continental-1.B.3/mcdg-list.qmd")
load(here::here("Rdata/20150130_EcoVeg_hierarchy.rda"))
load(here::here("Rdata/20181123_MacrogroupsCountry.rda"))

Macrogroups.Global |> filter(IVC.macrogroup_key == "M663") |>
  select(IVC.Name, Overall.Category, Overall.Bounds, Threat.criteria ) |>
  t() |>
  knitr::kable()
```

## Description

Description of this macrogroup is available at [NatureServe Explorer](https://explorer.natureserve.org/Taxon/ELEMENT_GLOBAL.2.884818/Valdivian_Temperate_Flooded_Swamp_Forest_Macrogroup).

Please note the changes in code and nomenclature between the version used for the assessment (in this website) and the current values in the NatureServe database.

### Characteristic biota

```{r}
load(here::here("Rdata/20210807_Macrogroup_characteristic_biota.rda"))
biota <- characteristic_biota |> filter(mg_key %in% "M663")
```

The list of characteristic biota includes `r nrow(biota)` plant species:

```{r}
#| results: asis
biota |> head(20) |> pull(species_name) |>
  paste(collapse = "; ") |>
  cat()
```


### Geographical distribution

Geospatial vector data for this macrogroup is available from @Ferrer-Paris_2024_OSF_vectordata.

This macrogroup is present in the following countries and territories:

```{r}
#| results: asis
Macrogroups.Country |> 
  filter(IVC.macrogroup_key == "M663") |> 
  pull(Country) |>
  paste(collapse = "; ") |>
  cat()
```

## RLE Assessment -- 2019 

This section summarises the results from @Ferrer-Paris_2019_RLE_Forests for this macrogroup.

### Validation of distribution

Prior to the RLE assessment, the distribution data for this macrogroup was validated with following results:

```{r}
load(here::here("Rdata/20210807_Macrogroup_validation_data.rda"))
full_validation_table |> 
  filter(`Macrogroup code` %in% "M663") |> 
  t() |>
  knitr::kable()
  
```


### Results by subcriterion

```{r}

Macrogroups.Global |> filter(IVC.macrogroup_key == "M663") |>
  select(A1:D3) |>
  t() |>
  knitr::kable()
```

