---
title: IUCN Red List of Ecosystem assessment for the forest macrogroups of the Americas
subtitle: Upload tables to postgres database
author: JR Ferrer-Paris
---

# Tables for the IUCN RLE assessment

We source these files to set up the database connection information:

```{r}
source $HOME/proyectos/IUCN/RLE-forests-panam-results/env/project-env.sh
```

We create a schema for the IUCN RLE assessment:

We use `R` for extracting data from the tables and translating to the PostgreSQL database. First we will add information on the assessment in a table

`psql -h $DBHOST -d $DBNAME -U $DBUSER`

```sql

CREATE SCHEMA ivc_rle;

CREATE TABLE ivc_rle.divisions (
  ev_key character varying(4),
  code text PRIMARY KEY,
  name text,
  fcode text,
  formation text,
  scode text,
  subclass text,
  ccode text,
  class text
);

CREATE TABLE ivc_rle.macrogroups (
  mg_key character varying(4) PRIMARY KEY,
  code text,
  name text,
  parent text
);
ALTER TABLE ivc_rle.macrogroups
  ADD CONSTRAINT ev_fkey
  FOREIGN KEY (parent)
  REFERENCES ivc_rle.divisions(code)
  ON DELETE CASCADE ON UPDATE CASCADE;

CREATE TABLE ivc_rle.assessment (
   mg_key character varying(4),
   country text,
   ref_code text,
   assessment_date date,
   a1 text[],
   a2b text[],
   a3  text[],
   b1 text[],
   b2 text[],
   b3  text[],
   b_conds text[],
   c2a  text[],
   c2b  text[],
   d1 text[],
   d2b text[],
   d3 text[],
   category  text[],
   threat_criteria text[],

   CONSTRAINT asmcode PRIMARY KEY (mg_key,country,assessment_date)
);


ALTER TABLE ivc_rle.assessment
  ADD CONSTRAINT mg_fkey
  FOREIGN KEY (mg_key)
  REFERENCES ivc_rle.macrogroups(mg_key)
  ON DELETE CASCADE ON UPDATE CASCADE;

```



For all criteria we will include best estimates and plausible bounds as an array. Best estimate is always the first value.

```{r}
#!R --vanilla
require(dplyr)
library(tidyr)
require(magrittr)
require(RPostgreSQL)

source("~/proyectos/IUCN/RLE-forests-panam-results/env/project-env.R")


## working directory and path to scripts
script.dir <- Sys.getenv("SCRIPTDIR")
setwd(script.dir)

drv <- dbDriver("PostgreSQL")
con <- dbConnect(drv, dbname = Sys.getenv("DBNAME"),
                 host = Sys.getenv("DBHOST"),
                 port = Sys.getenv("DBPORT"),
                 user = Sys.getenv("DBUSER"))

## Assessment outcomes
load(sprintf("%s/Rdata/%s_EcoVeg_hierarchy.rda",script.dir,"20150130"))

a1 <- EcoVeg_typology_hierarchy %>% filter(level %in% 'division') %>% transmute(ev_key=EV_key,code,name,fcode=parent)
a2 <- EcoVeg_typology_hierarchy %>% filter(level %in% 'formation') %>% transmute(fcode=code,formation=name,scode=parent)
a3 <- EcoVeg_typology_hierarchy %>% filter(level %in% 'subclass') %>% transmute(scode=code,subclass=name,ccode=parent)
a4 <- EcoVeg_typology_hierarchy %>% filter(level %in% 'class') %>% transmute(ccode=code,class=name)

division_table <- a1 %>% left_join(a2,by='fcode') %>% left_join(a3,by='scode') %>% left_join(a4,by='ccode')

dbWriteTable(con,"tmptable3",division_table,overwrite=T,row.names = FALSE)
qry <- "INSERT INTO ivc_rle.divisions SELECT * FROM tmptable3 ON CONFLICT (code) DO NOTHING"
dbSendQuery(con,qry)
qry <- "DROP TABLE tmptable3"
dbSendQuery(con,qry)


macrogrup_table <- EcoVeg_typology_hierarchy %>% filter(level %in% 'macrogroup') %>% transmute(mg_key=EV_key,code,name,parent)

dbWriteTable(con,"tmptable3",macrogrup_table,overwrite=T,row.names = FALSE)
qry <- "INSERT INTO ivc_rle.macrogroups SELECT * FROM tmptable3 ON CONFLICT (mg_key) DO NOTHING"
dbSendQuery(con,qry)
qry <- "DROP TABLE tmptable3"
dbSendQuery(con,qry)


load(sprintf("%s/Rdata/20181123_MacrogroupsCountry.rda", script.dir))

 Macrogroups.Global %>%transmute(
    mg_key=IVC.macrogroup_key,
    country=Country,
    a1=sprintf("'{%s}'",ifelse(is.na(bounds.A1),A1,
    paste(A1,gsub(" -- ",",",bounds.A1),sep=","))),
    a2b=sprintf("'{%s}'",ifelse(is.na(bounds.A2b),A2b,
    paste(A2b,gsub(" -- ",",",bounds.A2b),sep=","))),
    a3=sprintf("'{%s}'",ifelse(is.na(bounds.A3),A3,
    paste(A3,gsub(" -- ",",",bounds.A3),sep=","))),
    b1=sprintf("'{%s}'",B1),b2=sprintf("'{%s}'",B1),b3=sprintf("'{%s}'",B1),
    c2a=sprintf("'{%s}'",ifelse(is.na(bounds.C2a),C2a,
    paste(C2a,gsub("--",",",bounds.C2a),sep=","))),
    c2b=sprintf("'{%s}'",C2b),
   d1=sprintf("'{%s}'",D1),
    d2b=sprintf("'{%s}'",D2b),
    d3=sprintf("'{%s}'",D3),
    category=sprintf("'{%s}'",ifelse(is.na(Overall.Bounds),Overall.Category,
    paste(Overall.Category,gsub(" -- ",",",Overall.Bounds),sep=","))),
    threat_criteria=ifelse(is.na(Threat.criteria),"NULL",sprintf("'{%s}'", Threat.criteria))) -> Assessment

qry <- sprintf("INSERT INTO ivc_rle.assessment (mg_key,country,ref_code,assessment_date,a1,a2b,a3,b1,b2,b3,c2a,c2b,d1,d2b,d3,category,threat_criteria) values %s",
   paste( with(Assessment,sprintf("('%s','%s','Ferrer-Paris et al. 2019','2018-12-01',%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s)",mg_key,country,a1,a2b,a3,b1,b2,b3,c2a,c2b,d1,d2b,d3,category,threat_criteria)),collapse=","))

dbSendQuery(con,qry)


 Macrogroups.Country %>%transmute(
    mg_key=IVC.macrogroup_key,
    country=Country,
    a1=sprintf("'{%s}'",ifelse(is.na(bounds.A1),A1,
    paste(A1,gsub(" -- ",",",bounds.A1),sep=","))),
    a2b=sprintf("'{%s}'",ifelse(is.na(bounds.A2b),A2b,
    paste(A2b,gsub(" -- ",",",bounds.A2b),sep=","))),
    a3=sprintf("'{%s}'",ifelse(is.na(bounds.A3),A3,
    paste(A3,gsub(" -- ",",",bounds.A3),sep=","))),
    b1=sprintf("'{%s}'",B1),b2=sprintf("'{%s}'",B1),b3=sprintf("'{%s}'",B1),
    c2a=sprintf("'{%s}'",ifelse(is.na(bounds.C2a),C2a,
    paste(C2a,gsub("--",",",bounds.C2a),sep=","))),
    c2b=sprintf("'{%s}'",C2b),
   d1=sprintf("'{%s}'",D1),
    d2b=sprintf("'{%s}'",D2b),
    d3=sprintf("'{%s}'",D3),
    category=sprintf("'{%s}'",ifelse(is.na(Overall.Bounds),Overall.Category,
    paste(Overall.Category,gsub(" -- ",",",Overall.Bounds),sep=","))),
    threat_criteria=ifelse(is.na(Threat.criteria),"NULL",sprintf("'{%s}'", Threat.criteria))) -> Assessment

qry <- sprintf("INSERT INTO ivc_rle.assessment (mg_key,country,ref_code,assessment_date,a1,a2b,a3,b1,b2,b3,c2a,c2b,d1,d2b,d3,category,threat_criteria) values %s",
   paste( with(Assessment,sprintf("('%s','%s','Ferrer-Paris et al. 2019','2018-12-01',%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s,%s)",mg_key,country,a1,a2b,a3,b1,b2,b3,c2a,c2b,d1,d2b,d3,category,threat_criteria)),collapse=","))

dbSendQuery(con,qry)
dbDisconnect(con)

```

Replicate these values to be updated later
```sql
INSERT INTO ivc_rle.assessment
SELECT mg_key,country,'Imperiled, MS','2021-04-01',a1,a2b,a3,b1,b2,b3,b_conds,c2a,c2b,d1,d2b,d3,category,threat_criteria FROM ivc_rle.assessment where country='global' AND ref_code='Ferrer-Paris et al. 2019'
```


This is the list of mg_keys for dry forests (including Paleotropical ones):

```sql
select string_agg(mg_key::varchar,',' ORDER BY mg_key) from ivc_rle.macrogroups WHERE parent like '1.A.1%' ;
-- not needed here:
-- update ivc_americas set macrogroup='Cerradão Sclerophyllous Woodland' where value=872;
```
